Lesson 4
========================================================
```{r}

getwd()
setwd('~/WorkSpace/Udemy-Datascience/IntroductionToDataScience/EDA-DataAnalyse/L4')
```

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv',sep = '\t')
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point()
qplot(x = age, y = friend_count, data = pf)

summary(pf$age)


```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point()
qplot(x = age, y = friend_count, data = pf)

summary(pf$age)


```

***

### Overplotting
Notes:

```{r Overplotting}

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter( alpha =  1/20) + xlim(13,90)

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point( alpha =  1/20 , position = position_jitter(h = 0 )) + xlim(13,90) +
  coord_trans( y = 'sqrt')



ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point( alpha =  1/20 ) + xlim(13,90) +
  coord_trans( y = 'sqrt')

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point( alpha =  1/20 , position = position_jitter(h = 0 )) + xlim(13,90) +
  coord_trans( y = 'sqrt')

```

#### What do you notice?
Show better distribution.
***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

summary(pf$age)
summary(sqrt(pf$friendships_initiated))

ggplot(aes(x = age, y = friendships_initiated), data = pf) + geom_point()

ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
 geom_point( alpha =  1/20 , position = position_jitter(h = 0 )) +
  xlim(13,113) +coord_trans( y = 'sqrt')



```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
install.packages('dplyr')
library(dplyr)
# filtergroup_by mutate arrange

group_by(pf,age)
summary(pf$age)

age_groups <- group_by(pf, age)

age_groups

pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n() ) #number of user each group
pf.fc_by_age <- arrange(pf.fc_by_age, age)
head(pf.fc_by_age)

pf.fc_by_age <- pf %.%
  group_by(age) %.%
  summarise(friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n() ) %.%
  arrange(age)

head(pf.fc_by_age,20)

```

Create your plot!

```{r Conditional Means Plot}

ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) + 
 geom_line()

ggplot(aes(x = age, y = friend_count_median), data = pf.fc_by_age) + 
 geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

ggplot(aes(x = age, y = friend_count), data = pf) + 
   xlim(13,90) +
  geom_point( alpha =  1/20 , 
              position = position_jitter(h = 0 ),
              color ='orange') +
  coord_trans( y = 'sqrt') + 
  geom_line( stat = 'summary', fun.y = mean)+ 
  geom_line( stat = 'summary', fun.y = quantile, fun.args = list(probs = .1) ,linetype = 2 , color = 'blue')+ 
  geom_line( stat = 'summary', fun.y = quantile, fun.args = list(probs = .5) ,linetype = 1 , color = 'blue')+ 
  geom_line( stat = 'summary', fun.y = quantile, fun.args = list(probs = .9) ,linetype = 2 , color = 'blue')
  
ggplot(aes(x = age, y = friend_count), data = pf) + 
   coord_cartesian( xlim = c(13,70), ylim = c(0,1000))+
  geom_point( alpha =  1/20 , 
              position = position_jitter(h = 0 ),
              color ='orange') + 
  geom_line( stat = 'summary', fun.y = mean)+ 
  geom_line( stat = 'summary', fun.y = quantile, fun.args = list(probs = .1) ,linetype = 2 , color = 'blue')+ 
  geom_line( stat = 'summary', fun.y = quantile, fun.args = list(probs = .5) ,linetype = 1 , color = 'blue')+ 
  geom_line( stat = 'summary', fun.y = quantile, fun.args = list(probs = .9) ,linetype = 2 , color = 'blue')
```

#### What are some of your observations of the plot?
Response:

***
Friend_count in  age range (13,25) and (80,90) are familiar.
There are weird spike around  age 65-70.
Person who has friend count > 1000 quiet rare.

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
?cor.test

cor(pf$age, pf$friend_count)
cor.test(pf$age,pf$friend_count, methods = 'pearson')
with(pf,cor.test(pf$age,pf$friend_count, methods = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response: -0.02740737 not close to 1 or -1  so they are not related.

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf,pf$age <= 70), cor.test(age, friend_count, method = 'pearson'))
with(subset(pf,pf$age <= 70), cor.test(age, friend_count, method = 'spearman'))

```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
summary(sqrt(pf$www_likes_received))
summary(sqrt(pf$likes_received))
pf$www_likes_received
pf$likes_received
ggplot(aes(x = www_likes_received, y = likes_received), data = pf)+
  geom_point( alpha =  0.05 , color ='orange')+scale_x_log10()+scale_y_log10()


```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
?geom_smooth
ggplot(aes(x = www_likes_received, y = likes_received), data = pf)+
  geom_point()+
  xlim(0,quantile(pf$www_likes_received, 0.95)) +
  ylim(0,quantile(pf$www_likes, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')



```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
with(pf, cor.test(likes_received, www_likes_received, method = 'pearson'))
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data("Mitchell")
?Mitchell
head(Mitchell)
```

Create your plot!

```{r Temp vs Month}
summary(Mitchell$Temp)
ggplot(aes(y=Temp,x=Month),data = Mitchell) + geom_point()

ggplot(aes(y=Temp,x=Month),data = Mitchell) + geom_line()

ggplot(aes(y=Temp,x=Month),data = Mitchell) + geom_point()+xlim(0,12)


```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month,Mitchell$Temp)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

ggplot(aes(y=Temp,x=Month),data = Mitchell) + geom_point()+
  scale_x_discrete(breaks = seq(0,203,12))

ggplot(aes(y=Temp,x=Month%%12),data = Mitchell) + geom_point()+
  scale_x_discrete(breaks = seq(0,203,12))
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(data = pf.fc_by_age, aes(x=age , y = friend_count_mean))+ 
  geom_line()
head(pf.fc_by_age,10)
pf.fc_by_age[17:19,]
pf$age_with_months <- pf$age +(12-pf$dob_month)/12
pf$age_with_months

```

***

### Age with Months Means

```{r Age with Months Means}
age_month_group <-group_by(pf,age_with_months)
pf.fc_by_age_months <- summarise(age_month_group,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n() ) #number of user each group

pf.fc_by_age_months <- arrange(pf.fc_by_age_months, age_with_months)

head(pf.fc_by_age_months)

```

Programming Assignment
```{r Programming Assignment}
p1 <- ggplot(aes(x = age_with_months, y = friend_count_mean), data = subset(pf.fc_by_age_months,pf.fc_by_age_months$age_with_months < 71)) + 
 geom_line()


```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}


library(gridExtra)
p1 <- ggplot(aes(x = age_with_months, y = friend_count_mean), data = subset(pf.fc_by_age_months,pf.fc_by_age_months$age_with_months < 71)) + 
 geom_line() + geom_smooth()

p2 <- ggplot(aes(x = age, y = friend_count_mean), data = subset(pf.fc_by_age,pf.fc_by_age$age < 71)) + 
 geom_line()+ geom_smooth()

p3 <- ggplot(aes(x = round(age/5)*5, y = friend_count), data = subset(pf,pf$age < 71)) + 
 geom_line(stat = 'summary', fun.y= mean)

grid.arrange(p2,p1,p3,ncol=1)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!


PS4 : 
1 price vs. x
```{r}
diamonds
by(diamonds$price, diamonds$x, summary)
ggplot(data = diamonds,aes(x= x,y=price)) + geom_point()

```
2. Variable x positively exponential relate with variable price.
3 Correlation
```{r}
cor.test(diamonds$x,diamonds$price)
#0.8844352 
cor.test(diamonds$y,diamonds$price)
#0.8654209 
cor.test(diamonds$z,diamonds$price)
#0.8612494 

```

4 price vs depth
```{r}
?diamonds
names(diamonds)
#depth: total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43–79)
ggplot(data = diamonds,aes(x=depth ,y=price)) + geom_point(alpha = 0.01) 
```
5 Adjustment price vs dept
```{r}
summary(diamonds$depth)
ggplot(data = diamonds,aes(x=depth ,y=price)) + geom_point(alpha = 0.01) +
  scale_x_continuous(breaks = seq(43,79,2))

```

6 Typical Depth Range
Base on the catterplot of depth vs price most diamonds are between what value of depth?
Ans : 61 - 63

7 Correlation - price and depth
```{r}
cor.test(diamonds$depth,diamonds$price)
# ANS : According to the correlation result it show that there is no relation between them.
```
8. price vs carat

```{r}

summary(diamonds$price)
summary(diamonds$carat)
top_one_percent_price = quantile(diamonds$price,.99)
ggplot(data = subset(diamonds,diamonds$price > top_one_percent_price),aes(x=carat ,y=price)) + geom_point(alpha = 1) 
#the x-axis for carat extend past 2.
```

9. price vs. volume

```{r}

summary(diamonds$price)
diamonds$volume <- diamonds$x*diamonds$y*diamonds$z
summary(diamonds$volume)
ggplot(data = diamonds,aes(x=volume ,y=price)) + geom_point() 
#the x-axis for carat extend past 2.
```
10. Findings - price vs. volume
```{r}
library('plyr')

is.numeric(diamonds$volume)
count(diamonds$volume == 0) 
summary(diamonds$volume)
ggplot(data = diamonds,aes(x=volume ,y=price)) + geom_point() + xlim(0,1080)
detach("package:plyr", unload=TRUE)

# The plot show the highly exponential relation between them.
# There are 0 volume daimonds.
# There are 900 volume daimonds which cheaper than 300 volume diamonds.

```
11. Correlations on Subsets
```{r}

filter_diamonds = subset(diamonds,diamonds$volume > 0 & diamonds$volume < 800)
cor.test(filter_diamonds$price,filter_diamonds$volume)
```

12. Adjustments - price vs. volume
```{r}

ggplot(data = filter_diamonds,aes(x=volume ,y=price)) + geom_point( alpha = 0.05 ) +
  geom_smooth()
# This plot may not suitable on diamonds volume greater than 300 because there are too small number of data that have volume greater than 300.
```
13. Mean Price by Clarity

```{r}
detach("package:plyr", unload=TRUE) 
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
data(diamonds)
diamonds

diamonds_clarity_group <- group_by(diamonds,clarity)
diamonds_clarity_group
diamondsByClarity <- summarise(diamonds_clarity_group,
          mean_price = mean(price),
          median_price = median(price),
          min_price = min(price),
          max_price = max(price),
          n = n() ) #number of data each group

```
14. Bar Charts of Mean Price
Instructor Notes

Bar Charts vs. Histograms
# http://flowingdata.com/2014/02/27/how-to-read-histograms-and-use-them-in-r/

Hint: Save each plot into a variable and pass the two variables to grid.arrange(). Be sure you have installed and loaded the gridExtra package.
```{r}

library(dplyr)



diamonds_by_clarity <- group_by(diamonds, clarity)
diamonds_mp_by_clarity <- summarise(diamonds_by_clarity, mean_price = mean(price))

diamonds_by_color <- group_by(diamonds, color)
diamonds_mp_by_color <- summarise(diamonds_by_color, mean_price = mean(price))
#http://www.theanalysisfactor.com/r-11-bar-charts/
diamonds_mp_by_clarity

plot_bar_clarity <- ggplot(data = diamonds_mp_by_clarity,
                           aes(factor(clarity),y = mean_price) )+
                    geom_bar(stat = 'identity')
#plot_bar_clarity <- barplot(diamonds_mp_by_clarity$mean_price,ylab = "mean_price", xlab = "Clearity",
#                           names.arg = c("I1",  "SI2",  "SI1",  "VS2",  "VS1",  "VVS2",  "VVS1",  "IF"))
plot_bar_clarity
diamonds_mp_by_color
#plot_bar_color <- barplot(diamonds_mp_by_color$mean_price,ylab = "mean_price", xlab = "Clearity",
#                            names.arg = c("D",  "E",  "F",  "G",  "H",  "I",  "J"))

plot_bar_color <- ggplot(data = diamonds_mp_by_color,
                           aes(factor(color),y = mean_price) )+
                    geom_bar(stat = 'identity')
plot_bar_color
library(gridExtra)
grid.arrange(plot_bar_clarity,plot_bar_color,ncol =2)

?diamonds
#clarity: a measurement of how clear the diamond is (I1 (worst), SI1, SI2, VS1, VS2, VVS1, VVS2, IF (best))
#color: diamond colour, from J (worst) to D (best)

#By clarity SI2 give the highest mean price.
#By color J give the highest mean price.
#So this is weird.

```

15.  Trends in Mean Price
We think something odd is going here. These trends seem to go against our intuition.
Mean price tends to decrease as clarity improves. The same can be said for color.
We encourage you to look into the mean price across cut.

```{r}
#http://docs.ggplot2.org/0.9.3.1/geom_bar.html
ggplot(diamonds, aes(clarity, fill=color)) + geom_bar(position="dodge")
ggplot(diamonds, aes(clarity, fill=cut)) + geom_bar()


diamonds_by_cut <- group_by(diamonds, cut)
diamonds_mp_by_cut <- summarise(diamonds_by_cut, mean_price = mean(price))
ggplot(data = diamonds_mp_by_cut,
                           aes(factor(cut),y = mean_price) )+
                    geom_bar(stat = 'identity')

diamonds_by_cut_clarity <- group_by(diamonds, cut,clarity)
diamonds_mp_by_cut_clarity <- summarise(diamonds_by_cut_clarity, mean_price = mean(price))
diamonds_mp_by_cut_clarity

ggplot(diamonds_mp_by_cut_clarity, aes(x = clarity , fill=cut , y = mean_price)) + geom_bar(position="dodge",stat = 'identity')
```

16.Gapminder Revisited

I started with question if the having baby has any effect on Cervical or Breast cancer.
By this question I choose data:
"Cervical cancer, new cases per 100,000 women"
"Breast cancer, new cases per 100,000 women"
"Children per woman (total fertility)"
16.1 First I need to prepare dataframe to get inshape that easily to draw the plot.

```{r}

library(ggplot2)
library(xlsx)
library(dplyr)
library(tidyr)
#
cvix_cancer_data_raw <- read.xlsx("indicator cervix female incidence.xlsx", sheetIndex = 1)
names(cvix_cancer_data_raw)
cvix_cancer_data_2002 <- select(cvix_cancer_data_raw, one_of(c("Cervix.Female.Incidence", "X2002")))
cvix_cancer_data_2002<- rename(cvix_cancer_data_2002, country = Cervix.Female.Incidence)
cvix_cancer_data_2002<- rename(cvix_cancer_data_2002, cvix_cancer_no_per_100k = X2002)
names(cvix_cancer_data_2002)

breast_cancer_data_raw <- read.xlsx("indicator breast female incidence.xlsx", sheetIndex = 1)
names(breast_cancer_data_raw)
breast_cancer_data_2002 <- select(breast_cancer_data_raw, one_of(c("Breast.Female.Incidence", "X2002")))
breast_cancer_data_2002 <- rename(breast_cancer_data_2002, country = Breast.Female.Incidence)
breast_cancer_data_2002 <- rename(breast_cancer_data_2002, breast_cancer_no_per_100k = X2002)
names(breast_cancer_data_2002)

children_per_women_data_raw <- read.xlsx("indicator undata total_fertility.xlsx", sheetIndex = 1)
names(children_per_women_data_raw)
children_per_women_data_2002 <- select(children_per_women_data_raw, one_of(c("Total.fertility.rate", "X2002")))
children_per_women_data_2002 <- rename(children_per_women_data_2002, country = Total.fertility.rate)
children_per_women_data_2002 <- rename(children_per_women_data_2002, children_per_women = X2002)
names(children_per_women_data_2002)

data_all <- merge(cvix_cancer_data_2002, breast_cancer_data_2002)
data_all  <- merge(data_all, children_per_women_data_2002)
names(data_all)
data_all <- subset(data_all,!is.na(cvix_cancer_no_per_100k) & !is.na(breast_cancer_no_per_100k) & !is.na(children_per_women))
head(data_all)
ggplot(data_all,aes(x = children_per_women , y = breast_cancer_no_per_100k))+geom_point(alpha = 0.5)
ggplot(data_all,aes(x = children_per_women , y = cvix_cancer_no_per_100k))+geom_point(alpha = 0.5)

data_all <- subset(data_all,children_per_women <= 7)
cpw_groups <- group_by(data_all, children_per_women)
data_all.cancer_by_cpw <- summarise(cpw_groups,
          breast_cancer_mean = mean(breast_cancer_no_per_100k),
          cvix_cancer_mean = mean(cvix_cancer_no_per_100k),
          n = n() )
data_all.cancer_by_cpw <- arrange(data_all.cancer_by_cpw, children_per_women)

ggplot(aes(x = children_per_women, y = breast_cancer_mean), data = data_all.cancer_by_cpw) + 
 geom_line() + geom_smooth()
p1<- ggplot(aes(x = children_per_women, y = breast_cancer_mean), data = data_all.cancer_by_cpw) + 
 geom_line() + geom_smooth()

p2<- ggplot(aes(x = children_per_women, y = cvix_cancer_mean), data = data_all.cancer_by_cpw) + 
 geom_line() + geom_smooth()
library(gridExtra)
grid.arrange(p2,p1,ncol=1)

with(data_all, cor.test(children_per_women, breast_cancer_no_per_100k))
with(data_all, cor.test(children_per_women, cvix_cancer_no_per_100k))

```

