Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:
```{r}

library(ggplot2)
setwd('~/WorkSpace/Udemy-Datascience/IntroductionToDataScience/EDA-DataAnalyse/L5')
pf <- read.csv('pseudo_facebook.tsv',sep = '\t')
suppressMessages(library(dplyr))

```

```{r Third Qualitative Variable}
hasgender_pf <- subset(pf, !is.na(gender))
hasgender_pf
ggplot(aes(x = friend_count),data = hasgender_pf)+ facet_wrap(~gender) + geom_histogram()
summary(pf$friend_count)

by(pf$age,pf$gender, summary)

ggplot(aes(x = gender, y = age),
       data = hasgender_pf) + geom_boxplot() 
ggplot(aes(x = gender, y = age),
       data = hasgender_pf) + geom_boxplot() + stat_summary(fun.y = mean, geom = 'point', shape = 4)
?aes #aesthetic mappings 
ggplot(aes(x = age,y=friend_count),data = hasgender_pf)+ 
  geom_line(aes(color = gender) ,stat = 'summary', fun.y = 'median')

library(dplyr)
hasgender_pf <- subset(pf, !is.na(gender))
pf_group_age_gender <- group_by(hasgender_pf,age,gender)
pf.fc_by_age_gender <- summarise(pf_group_age_gender,
          mean_friend_count = mean(friend_count),
          median_friend_count = median(friend_count),
          n = n() ) #number of user each group
pf.fc_by_age_gender <- arrange(pf.fc_by_age_gender, age)
pf.fc_by_age_gender <- ungroup(pf.fc_by_age_gender)


```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}

ggplot(aes(x = age, y = mean_friend_count),
       data = pf.fc_by_age_gender) +geom_line( aes(color = gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***
```{r}
library(tidyr)
tidyr::spread(subset(pf.fc_by_age_gender, select = c('gender', 'age', 'median_friend_count')), gender, median_friend_count)

```

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)
pf.fc_by_age_gender
dcast(pf.fc_by_age_gender,age ~ gender,value.var = 'median_friend_count')

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var = 'median_friend_count')
head(pf.fc_by_age_gender.wide)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
# Plot the ratio of the female to male median
# friend counts using the data frame
# pf.fc_by_age_gender.wide.


# The linetype parameter can take the values 0-6:
# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash
ggplot(aes(x = age, y = female/male),
       data = pf.fc_by_age_gender.wide) + geom_line() +
        geom_hline(yintercept = 1 ,linetype = 2, alpha = 0.3)
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
# Create a variable called year_joined
# in the pf data frame using the variable
# tenure and 2014 as the reference year.
summary(pf$tenure)
pf$year_joined <- 2014 - ceiling(pf$tenure / 365)
pf$year_joined <- floor(2014 - (pf$tenure / 365))
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
table(pf$year_joined)

summary(pf$year_joined)
?cut
# Create a new variable in the data frame
# called year_joined.bucket by using
# the cut function on the variable year_joined.
c2 <- cut(pf$year_joined, breaks = 3)
table(c2)
pf$year_joined.bucket = cut(pf$year_joined,breaks = 3)
table(pf$year_joined.bucket)
pf$year_joined.bucket = cut(pf$year_joined,c(2004,2009,2011,2012,2014))

```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(pf$year_joined.bucket,useNA = 'ifany')


ggplot(aes(x = age,y=friend_count),data = hasgender_pf)+ 
  geom_line(aes(color = gender) ,stat = 'summary', fun.y = 'median')


ggplot(aes(x = age,y=friend_count),data = subset(pf,!is.na(year_joined.bucket)))+ 
  geom_line(aes(color = year_joined.bucket) ,stat = 'summary', fun.y = 'median')
```


***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}

ggplot(aes(x = age,y=friend_count),data = subset(pf,!is.na(year_joined.bucket)))+ 
  geom_line(aes(color = year_joined.bucket) ,stat = 'summary', fun.y = 'median') +
  geom_line(stat = 'summary', fun.y = 'mean',linetype = 2)


```

***

### Friending Rate
Notes:

```{r Friending Rate}
pf_has_tenure <- subset(pf,!is.na(tenure) & tenure > 0)
friend_rate <- pf_has_tenure$friend_count / pf_has_tenure$tenure
summary(friend_rate)

with(subset(pf, tenure > 0),summary(friend_count / tenure))
```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
  0.0000   0.0775   0.2205   0.6096   0.5658 417.0000 
```{r Friendships Initiated}

ggplot(aes(x = tenure,y=friendships_initiated/tenure),data = subset(pf,!is.na(year_joined.bucket) & tenure > 0))+ 
  geom_line(aes(color = year_joined.bucket) ,stat = 'summary', fun.y = 'mean')

ggplot(aes(x = 30*round(tenure/30),y=friendships_initiated/tenure),data = subset(pf,!is.na(year_joined.bucket) & tenure > 0))+ 
  geom_line(aes(color = year_joined.bucket) ,stat = 'summary', fun.y = 'mean')

ggplot(aes(x = tenure,y=friendships_initiated/tenure),data = subset(pf,!is.na(year_joined.bucket) & tenure > 0))+ 
  geom_smooth(aes(color = year_joined.bucket) )

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo <- read.csv("yogurt.csv")
str(yo)
yo$id = factor(yo$id)
str(yo)
ggplot(aes(x = price),data = yo) + geom_histogram(binwidth = 10 ,fill = 'grey')

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
summary(yo)
length(unique(yo$price))
table(yo$price)
?transform
# Create a new variable called all.purchases,
# which gives the total counts of yogurt for
# each observation or household.
yo <- transform(yo,all.purchases = strawberry+blueberry+pina.colada+plain+mixed.berry )
summary(yo)

```

***

### Prices over Time
Notes:

```{r Prices over Time}

ggplot(aes(x= time,y = price),data = yo) + geom_point(alpha = 0.1)
ggplot(aes(x= time,y = price),data = yo) + geom_jitter(alpha =0.25 ,shape = 21,fill = '#e7ad61')
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

# Set the seed for reproducible results
set.seed(12345)
sample.ids <- sample(levels(yo$id),16)
sample.ids

sample(levels(yo$id),16)
sample(levels(yo$id),16)

ggplot(aes(x=time,y = price), 
       data = subset(yo, id %in% sample.ids))+
      facet_wrap(~id) +
  geom_line()+
  geom_point(aes(size = all.purchases),pch = 1 )
?geom_point
#Use the pch or shape parameter to specify the symbol when plotting points. Scroll down to 'Plotting Points' on QuickR's Graphical Parameters.
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***
```{r}
#install.packages('GGally')
library(GGally)
theme_set(theme_minimal(20))
set.seed(1836)
pf_subset <-pf[,c(2:15)]
names(pf)
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])

samples_pf <- pf_subset[sample.int(nrow(pf_subset),1000),]

cor.test(samples_pf$friend_count,samples_pf$friendships_initiated)
cor.test(samples_pf$age,samples_pf$mobile_likes)


```


### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
names(nci)
head(nci)
colnames(nci) <- c(1:64)
?colnames #Retrieve or set the row or column names of a matrix-like object.

colnames(nci)
```

```{r}

library(reshape2)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
nrow(nci[1:200,])
#64*200
nrow(melt(as.matrix(nci[1:200,])))
?as.matrix
?melt# Melt an object into a form suitable for easy casting.

head(nci.long.samp)
as.matrix(nci[1:10,])
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

