RedwineQuality by Pasit Nusso
=================================



# Analysis

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(GGally)
library(gridExtra)
```
   
```{r echo=FALSE, Load_the_Data}
# Load the Data

setwd("~/WorkSpace/Udemy-Datascience/IntroductionToDataScience/P4-EDA/")
redwine_data <- read.csv(file = "wineQualityReds.csv")

redwine_data$X <- NULL
```


# Univariate Plots Section

```{r echo=FALSE}

str(redwine_data)
summary(redwine_data)

```
Most wine's quality is 6 and range is 3 to 8. The mean of alcohol is 10.42.

```{r echo=FALSE, warning=FALSE, fixed.acidity}
feature<-redwine_data$fixed.acidity
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.5)+
    scale_x_continuous(lim = c(4,16), breaks = seq(4,16,0.5))+
  xlab('fixed.acidity (g / cm^3)') + ylab('frequency')
summary(feature)

```
The volatile.acidity distribution is normal. The median is 7.9.

```{r echo=FALSE, warning=FALSE, volatile.acidity}
feature<-redwine_data$volatile.acidity
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.02)+
  scale_x_continuous(lim = c(0,1.6), breaks = seq(0,1.6,0.05))+
  xlab('volatile.acidity (g / cm^3)') + ylab('frequency')
summary(feature)

```
The volatile.acidity distribution is bimodal with the volatile.acidity peaking at 0.4, 0.5 and 0.6.
 
 
```{r echo=FALSE, warning=FALSE, citric.acid}

feature<-redwine_data$citric.acid
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.01)+
  scale_x_continuous(lim = c(0,0.75), breaks = seq(0,0.75,0.02))+
  xlab('citric.acid (g / dm^3)') + ylab('frequency')
summary(feature)
table(feature)
```
 The distribution for citric acid appears bimodal with the peaking at 0, 0.24, 0.49.
 
```{r echo=FALSE, warning=FALSE, residual.sugar}

feature<-redwine_data$residual.sugar
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.1)+
  xlab('residual.sugar (g / cm^3)') + ylab('frequency')
summary(feature)
table(feature)
```
```{r echo=FALSE, warning=FALSE, residual.sugarlog.10}

feature<-redwine_data$residual.sugar
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.024)+
  scale_x_log10()+
  xlab('residual.sugar (g / cm^3)') + ylab('frequency')
summary(feature)
table(feature)
quantile(feature,.9)
```
Transform the long tail data to better understand the distribution of residual.sugar
The distribution for residual.sugar appears to be right skewed. Most of them (90%) residual.sugar less  than 3.6 (4.5 g / cm^3 are considered sweet).
 
```{r echo=FALSE, warning=FALSE, chlorides}

feature<-redwine_data$chlorides
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.002)+
  xlab('chlorides (g / cm^3)') + ylab('frequency')

```

```{r echo=FALSE, warning=FALSE, chlorides.log.10}

ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.024)+
  scale_x_log10()+
  xlab('chlorides (g / cm^3)') + ylab('frequency')
summary(feature)
quantile(feature,.95)

```
Transform the long tail data to better understand the distribution of chlorides
The distribution for chlorides appears to be right skewed. Most of them (95%) chlorides less than 0.1261 .


```{r echo=FALSE, warning=FALSE, free.sulfur.dioxide}

feature<-redwine_data$free.sulfur.dioxide
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 2)+
  xlab('free.sulfur.dioxide  (mg / dm^3)') + ylab('frequency')
summary(feature)
quantile(feature,.95)

```
```{r echo=FALSE, warning=FALSE, sqrt.free.sulfur.dioxide }
?trans_breaks
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.4)+
  scale_x_sqrt(lim = c(1,80),breaks = seq(0,100,1))+
  xlab('free.sulfur.dioxide (mg / dm^3)') + ylab('frequency')
summary(feature)
quantile(feature,.95)

```
Transform the long tail data to better understand the distribution of free.sulfur.dioxide
The free.sulfur.dioxide distribution is bimodal with the free.sulfur.dioxide peaking at 7 and 17.
 


```{r echo=FALSE, warning=FALSE, total.sulfur.dioxide}

feature<-redwine_data$total.sulfur.dioxide
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 2)+
  xlab('total.sulfur.dioxide  (mg / dm^3)') + ylab('frequency')
summary(feature)
quantile(feature,.95)

```
```{r echo=FALSE, warning=FALSE, total.sulfur.dioxidelog.10}
?trans_breaks
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.1)+
  scale_x_log10(lim = c(1,200),breaks = seq(0,200,2))+
  xlab('total.sulfur.dioxide (mg / dm^3)') + ylab('frequency')
summary(feature)
quantile(feature,.95)

```
Transform the long tail data to better understand the distribution of total.sulfur.dioxide
The total.sulfur.dioxide distribution is normal.
 

```{r echo=FALSE, warning=FALSE, pH}

feature<-redwine_data$pH
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.02)+
  xlab('pH)') + ylab('frequency')
summary(feature)
table(feature)
```
The pH distribution is normal.

```{r echo=FALSE, warning=FALSE, density}

feature<-redwine_data$density
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.001)+
  scale_x_continuous(lim = c(0.990,1.005), breaks = seq(0.990,1.005,0.0005))+
  xlab('Density (g / cm^3)') + ylab('frequency')
summary(feature)
```
 The distribution for density acid appears to be normal and the different between min and max is only 0.014. ( different between alcohol and water is 0.22)
 
 Ref : https://en.wikipedia.org/wiki/Ethanol
 
```{r echo=FALSE, warning=FALSE, sulphates}

feature<-redwine_data$sulphates
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.04)+
  scale_x_continuous(lim = c(0.3,2.0), breaks = seq(0.3,2.0,0.04))+
  xlab('Sulphates (potassium sulphate - g / dm3)') + ylab('frequency')


```

```{r echo=FALSE, warning=FALSE, log10.sulphates }

feature<-redwine_data$sulphates

ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.04)+
  scale_x_log10()+
  xlab('Sulphates (potassium sulphate - g / dm3)') + ylab('frequency')
summary(feature)
quantile(feature,.95)
```
Transform the long tail data to better understand the distribution of sulphates.
The distribution for sulphates appears to be normal. Most of them (95%) sulphates less than 0.93.

 
```{r echo=FALSE, warning=FALSE, alcohol}

feature<-redwine_data$alcohol
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.1)+
  scale_x_continuous(lim = c(8,13), breaks = seq(8,13,0.2))+
  xlab('alcohol (% by volume)') + ylab('frequency')

summary(feature)
```

The distribution for alcohol appears to be right skewed.


```{r echo=FALSE, warning=FALSE, quality}

feature<-redwine_data$quality
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 1)+
  xlab('WineQuality') + ylab('frequency')

table(feature)
nrow(subset(redwine_data,quality >4 & quality < 8)) / nrow(redwine_data)
```

Most of data's wine qulity is between 5 to 7 (94.9 %). I think I will covert this feature to factor for Multivariate Analysis.



# Univariate Analysis
 
### What is the structure of your dataset?

ANS :
There are 1599 wine in the data set with 12 features.
```{r echo=FALSE}
str(redwine_data)
summary(redwine_data)
head(redwine_data)
```

Input variables (based on physicochemical tests):
1. - fixed acidity (tartaric acid - g / dm^3): most acids involved with wine or fixed or nonvolatile (do not evaporate readily)
2. - *volatile acidity (acetic acid - g / dm^3): the amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste
3. - *citric acid (g / dm^3): found in small quantities, citric acid can add 'freshness' and flavor to wines
4. - residual sugar (g / dm^3): the amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with greater than 45 grams/liter are considered sweet
5. - chlorides (sodium chloride - g / dm^3): the amount of salt in the wine
6. - free sulfur dioxide (mg / dm^3): the free form of SO2 exists in equilibrium between molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial growth and the oxidation of wine
7. - *total sulfur dioxide (mg / dm^3): amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine
8. - *density (g / cm^3)
9. - pH: describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale
10. - sulphates (potassium sulphate - g / dm3): a wine additive which can contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial and antioxidant
11. - alcohol (% by volume): the percent alcohol content of the wine

Output variable (based on sensory data): 
12. - quality (score between 0 and 10)


### What is/are the main feature(s) of interest in your dataset?
ANS: The main feature of interest is wine's quality. I would like to investigate which variable(s) effect the wine quality.



### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?
ANS: I think smell taste touch and addictive content that will effect the wine's quality so the features that I choose for investigation is :

1) sulphates
2) volatile acidity
3) citric acidity
4) chlorides 
6) sum of acid (tartaric acid + citric acid ) as "sourness"
5) alcohol

```{r echo=FALSE}
#https://en.wikipedia.org/wiki/Taste
redwine_data$sourness = redwine_data$fixed.acidity*0.7 + redwine_data$citric.acid*0.46 
head(redwine_data)
```


### Did you create any new variables from existing variables in the dataset?

Yes, I create "sourness"  from fixed.acidity and citric.acid that represent the sourness of wine.

### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?


ANS: The distribution for citric acid, volatile.acidity and free.sulfur.dioxide appears bimodal and I tidies the data by remove X feature  that I am not interested and transform fixed.acidity and citric.acid to sourness for next investigation.


# Bivariate Plots Section
```{r echo=FALSE, Bivariate_Plots}

set.seed(1112)
data_all_subset <-redwine_data

sample.int(nrow(data_all_subset),100)
ggpairs(data_all_subset[,])

```

Top correlation values for quality is :
1. alcohol : 0.476
2. volatile.acidity : -0.391
3. sulphates : 0.251
4. citric acid : 0.226

```{r  echo=FALSE}
build_bivarate_plot <- function(data,x, y, ylab,xlab) {
  return (ggplot(data = data, aes(x = x, y = y)) + geom_boxplot() +  ylab(ylab) + xlab(xlab)
  )
}
redwine_data$wine_rating <- ifelse(redwine_data$quality <= 5, 'normal', ifelse( redwine_data$quality < 7, 'good', 'excellent'))
redwine_data$wine_rating <- ordered(redwine_data$wine_rating,levels = c('normal', 'good', 'excellent'))
```

```{r  echo=FALSE, WineQuality.vs.volatile.acidity}
feature <- redwine_data$volatile.acidity
feature_name <- 'volatile.acidity'
volatile.acid.V.wine_rating.plot<- build_bivarate_plot(redwine_data, redwine_data$wine_rating, feature ,feature_name,'wine_rating')+scale_y_continuous(lim = c(0,1.6), breaks = seq(0,1.6,0.05))
volatile.acid.V.wine_rating.plot
with(redwine_data, cor.test(feature, quality, method = 'pearson'))

```
### WineQuality.vs.citric.acid
```{r  echo=FALSE }
feature <- redwine_data$citric.acid
feature_name <- 'citric.acid'
citric.acid.V.wine_rating.plot<- build_bivarate_plot(redwine_data, redwine_data$wine_rating, feature ,feature_name,'wine_rating')
citric.acid.V.wine_rating.plot
with(redwine_data, cor.test(feature, quality, method = 'pearson'))

```

### WineQuality.vs.sulphates
```{r  echo=FALSE }
feature <- redwine_data$sulphates
feature_name <- 'sulphates'
sulphates.V.wine_rating.plot<-build_bivarate_plot(redwine_data, redwine_data$wine_rating, feature ,feature_name,'wine_rating')+
  scale_y_continuous(lim = c(0.25,1), breaks = seq(0.25,1,0.05))
sulphates.V.wine_rating.plot
with(redwine_data, cor.test(feature, quality, method = 'pearson'))


```


### WineQuality.vs.alcohol
```{r  echo=FALSE }
feature <- redwine_data$alcohol
feature_name <- 'alcohol'
alcohol.V.wine_rating.plot<-build_bivarate_plot(redwine_data, redwine_data$wine_rating, feature ,feature_name,'wine_rating')+scale_y_continuous(lim = c(8,15), breaks = seq(8,15,0.1))
with(redwine_data, cor.test(feature, quality, method = 'pearson'))
alcohol.V.wine_rating.plot
```


# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?
ANS: From the plots and correlation values sulphates, citric acid acidity, alcohol positively relate with quality but volatile acidity negatively relate with quality.

Alcohol sulphates and volatile acidity 's plot show the different between 3 wine rating of wine very well but citric acid show the different between normal and good wine poorly.


### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

```{r echo=FALSE,warning=FALSE, Multivariate_Plots}

build_bivarate_plot2 <- function(data,x, y, xlab,ylab) {
  return (
          ggplot(aes(x = x, y = citric.acid), data = data) +
            geom_point( alpha =  1/2 ) +
            xlab(xlab) + ylab(ylab)+
            geom_smooth()
  )
}

featureX <- redwine_data$volatile.acidity
featureX_name <- 'volatile.acidity'
featureY <- redwine_data$citric.acid
featureY_name <- 'citric.acid'

build_bivarate_plot2(redwine_data, featureX, featureY ,featureX_name , featureY_name)+
  scale_x_continuous(lim = c(0.1,1.2), breaks = seq(0.1,1.2,0.1))+
  scale_y_continuous(lim = c(0,0.9), breaks = seq(0,0.9,0.1))

with(redwine_data, cor.test(featureX, featureY, method = 'pearson'))

featureX <- redwine_data$sulphates
featureX_name <- 'sulphates'
featureY <- redwine_data$citric.acid
featureY_name <- 'citric.acid'

build_bivarate_plot2(redwine_data, featureX, featureY ,featureX_name , featureY_name)+
  scale_x_continuous(lim = c(0.1,1.2), breaks = seq(0.1,1.2,0.1))
with(redwine_data, cor.test(featureX, featureY, method = 'pearson'))

featureX <- redwine_data$alcohol
featureX_name <- 'alcohol'
featureY <- redwine_data$citric.acid
featureY_name <- 'citric.acid'

build_bivarate_plot2(redwine_data, featureX, featureY ,featureX_name , featureY_name)
with(redwine_data, cor.test(featureX, featureY, method = 'pearson'))


```
ANS: 
I found that citric acid and volatile acidity very correlate.  
  
#### High Corelation:  
citric acid and volatile acidity : -0.5524957  
citric acid and sulphates acidity : 0.31277   
  
#### Low Corelation:  
citric acid and alcohol acidity : 0.1099032  
  

### What was the strongest relationship you found?  
ANS: For feature of interest alcohol percentage has highest corelation value.(0.476)  
     For every pair of features free.sulfur.dioxide and total.sulfur.dioxide has highest corelation value. (0.66  
  


# Multivariate Plots Section


First I need to prepare alcohol.grade for multivariate plot.
```{r echo=FALSE}

redwine_data$alcohol.grade <- ifelse(redwine_data$alcohol < 10, 'low', ifelse( redwine_data$alcohol < 11.5, 'medium-low', 'medium'))
redwine_data$alcohol.grade <- ordered(redwine_data$alcohol.grade,levels = c('low', 'medium-low', 'medium'))
table(redwine_data$alcohol.grade)

```

```{r echo=FALSE, wine.rating.vs.Alcohol.vs.volatile.acidity }

ggplot(aes(x = volatile.acidity, y = alcohol,color = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('volatile.acidity') + ylab('% alcohol')+
  scale_x_continuous(lim = c(0,1.6), breaks = seq(0,1.6,0.05))+
  geom_point(alpha = 1/3,size =5)
```
  
From the plot show that excellent wine mostly stay on the top left, good wine stay in the middle and normal wine stay in the bottom right.



```{r echo=FALSE,warning=FALSE, wine.rating.vs.alcohol.grade.vs.volatile.acidity }

wine_rating.v.alcohol.grade.v.volatile.acidity.plot <- ggplot(aes(x = volatile.acidity ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('volatile.acidity') + ylab('frequency')+  scale_fill_brewer(type = 'qual')+
  scale_x_continuous(lim = c(0.1,1), breaks = seq(0.1,1,0.05))+
  geom_histogram()+facet_wrap(~alcohol.grade,ncol = 1, scales="free_y")
wine_rating.v.alcohol.grade.v.volatile.acidity.plot
```
  
Wine rating.vs.alcohol.grade.vs.volatile.acidity plot shows that :
  
excellent wine ratio in alcohol grade "medium" on volatile.acidity range 0.25-0.4 is very high.

```{r echo=FALSE,warning=FALSE, wine.rating.vs.alcohol.grade.vs.citric.acid }
names(redwine_data)
wine_rating.v.alcohol.grade.v.citric.acid.plot <- ggplot(aes(x = citric.acid ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('citric.acid') + ylab('frequency')+  scale_fill_brewer(type = 'qual')+
  scale_x_continuous(lim = c(0,0.9), breaks = seq(0,0.9,0.1))+
  geom_histogram()+facet_wrap(~alcohol.grade,ncol = 1, scales="free_y")
wine_rating.v.alcohol.grade.v.citric.acid.plot
```
  
Wine rating.vs.alcohol.grade.vs.citric.acid plot shows that excellent wine ratio in alcohol grade "medium" on citric.acid at 0 and 0.4 is very high.


```{r echo=FALSE,warning=FALSE, wine.rating.vs.alcohol.grade.vs.total.sulfur.dioxide }
names(redwine_data)
wine_rating.v.alcohol.grade.v.total.sulfur.dioxide.plot <- ggplot(aes(x = total.sulfur.dioxide ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('total.sulfur.dioxide') + ylab('frequency')+  scale_fill_brewer(type = 'qual')+
  geom_histogram()+facet_wrap(~alcohol.grade,ncol = 1, scales="free_y")+
  scale_x_continuous(lim = c(0,170), breaks = seq(0,170,5))
wine_rating.v.alcohol.grade.v.total.sulfur.dioxide.plot
```
  
Wine rating.vs.alcohol.grade.vs.total.sulfur.dioxide plot shows that excellent wine ratio in alcohol grade "medium" on total.sulfur.dioxide at 5-30 is very high.


```{r echo=FALSE,warning=FALSE, wine.rating.vs.alcohol.grade.vs.sulphates }

wine_rating.v.alcohol.grade.v.sulphates.acidity.plot <- ggplot(aes(x = sulphates ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('sulphates') + ylab('frequency')+  scale_fill_brewer(type = 'qual')+
  scale_x_continuous(lim = c(0.35,1), breaks = seq(0.35,1,0.05))+
  geom_histogram()+facet_wrap(~alcohol.grade,ncol = 1, scales="free_y")
wine_rating.v.alcohol.grade.v.sulphates.acidity.plot

```
  
Wine rating.vs.alcohol.grade.vs.sulphates plot shows that excellent wine ratio in alcohol grade "medium" on sulphates range 0.7-0.9 is very high.


```{r echo=FALSE,warning=FALSE, wine.rating.vs.alcoholgrade.vs.sourness.vs.chlorides  }

wine_rating.v.alcohol.grade.v.sourness.chlorides.plot <- ggplot(aes(x = sourness, y = chlorides,color = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('sourness') + ylab('chlorides')+
  geom_point(alpha = 1/3,size =3)+facet_wrap(~alcohol.grade,ncol = 1)
wine_rating.v.alcohol.grade.v.sourness.chlorides.plot
  

```
    
Pattern is not noticable here.  


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

From the plots , show that alcohol feature is the highest impact feature.  

Wine rating.vs.alcohol.grade.vs.volatile.acidity plot shows that excellent wine ratio in alcohol grade "medium" on volatile.acidity range 0.25-0.4 is very high.  
Wine rating.vs.alcohol.grade.vs.citric.acid plot shows that excellent wine ratio in alcohol grade "medium" on citric.acid at 0 and 0.35-0.5 is very high.  
Wine rating.vs.alcohol.grade.vs.total.sulfur.dioxide plot shows that excellent wine ratio in alcohol grade "medium" on total.sulfur.dioxide at 5-30 is very high.  
Wine rating.vs.alcohol.grade.vs.sulphates plot shows that excellent wine ratio in alcohol grade "medium" on sulphates range 0.7-0.9 is very high.  
Win rating.vs.alcohol.grade.vs.sourness.vs.chlorides shows that there hardly to determine wine quality by tongue (chorides and sourness).  


### Were there any interesting or surprising interactions between features?  

It is very surprise that smell(total.sulfur.dioxide) has influnce over the wine rating but taste(chorides and sourness) has not.  


------

# Final Plots and Summary

### Plot One 


```{r echo=FALSE, Plot_One : Alcohol.distribution}

feature<-redwine_data$alcohol
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.1, color = I('black'), fill = I('#F79420') )+
  scale_x_continuous(lim = c(8,13), breaks = seq(8,13,0.2))+
  xlab('alcohol (% by volume)') + ylab('frequency')

```
 
### Description One

 The distribution for alcohol appears right skewed with the peaking at 0, 0.95, may be since the demand of wine are tend to be lower on higher percent alcohol wine.

### Plot Two
```{r echo=FALSE,warning=FALSE, Plot_Two}
grid.arrange(alcohol.V.wine_rating.plot,sulphates.V.wine_rating.plot,citric.acid.V.wine_rating.plot,volatile.acid.V.wine_rating.plot)
```

### Description Two

Alcohol percentage, Sulphates, Volatile acidity correlate with wine rating positively but Volatile acidity correlate negatively.  
The alcohol variance in wine rating good and excellent are much larger than normal.  
The citric acid variance in wine rating good and normal are much larger than excellent.  


### Plot Three
```{r echo=FALSE,warning=FALSE,  Plot_Three}
wine_rating.v.alcohol.grade.v.volatile.acidity.plot  
wine_rating.v.alcohol.grade.v.citric.acid.plot  
wine_rating.v.alcohol.grade.v.total.sulfur.dioxide.plot  
wine_rating.v.alcohol.grade.v.sulphates.acidity.plot  
```

### Description Three

On low alcohol percentage wine exellent quality rarely to be found mostly is normal rating wine.  
On medium-low alcohol percentage wine exellent can be found on low volatile acidity and total sulfur dioxide below 55 but mostly are normal and good rating wine.  
On mediumw alcohol percentage wine exellent can be found at high percentage on total sulfur dioxide below 50 and sulphate upper than 0.65 and mostly are exellent and good rating wine.  
------

# Reflection

```{r echo=FALSE}
str(redwine_data)
```

The data set contain 1599 wine from 2009. I start by understand the variables in data set and try to interpret in term of sense that human can percieve. Surprisingly, I found that the taste sourness and salty has no evidence that they has influence over the quality of wine but the smell (total sulfur dioxide), addictive content (alcohol), voilatile acidity, citric acid and sulphates has influence over it. On low alcohol percentage we hardly found excellent wine_rating but mostly is normal and you can find some of good wine rating if they has total SO2 in range 5-60 and sulphates in range 0.53-0.73 ,On medium-low alcohol percentage wine exellent can be found on low volatile acidity and total sulfur dioxide below 55 but mostly are normal and good rating wine,On mediumw alcohol percentage wine exellent can be found at high percentage on total sulfur dioxide below 50 and sulphate upper than 0.65 and mostly are exellent and good rating wine.  
After I research and ask drinkers, I found that there are many significant variables we do not have such as type of grape, where it made from, age of wine.  
Anyway drink wine is an art, it is possible that the wine rating come from diffent drinker can be different value.  

