RedwineQuality by Pasit Nusso
=================================

```{r global_options, include=FALSE,echo=FALSE, message=FALSE,} 
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/', 
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(GGally)
library(gridExtra)
library(plyr)
```
   
```{r echo=FALSE, Load_the_Data}
# Load the Data

setwd("~/WorkSpace/Udemy-Datascience/IntroductionToDataScience/P4-EDA/")
redwine_data <- read.csv(file = "wineQualityReds.csv")

redwine_data$X <- NULL
names(redwine_data)
names(redwine_data)[6] <- c("free.SO2")
names(redwine_data)[7] <- c("total.SO2")
names(redwine_data)[4] <- c("sugar")
#names(redwine_data)[1] <- c("fix.acid")#fixed.acidity 
#names(redwine_data)[2] <- c("A.acid")#volatile.acidity
#names(redwine_data)[3] <- c("citric")#citric.acid
```


# Univariate Plots Section

```{r echo=FALSE}

str(redwine_data)
summary(redwine_data)

```
Most wine's quality is 6 and range is 3 to 8. The mean of alcohol is 10.42.

```{r echo=FALSE, warning=FALSE, fixed.acidity}
feature<-redwine_data$fixed.acidity
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.5)+
    scale_x_continuous(lim = c(4,16), breaks = seq(4,16,0.5))+
  xlab('fixed.acidity (g / cm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)

```
The volatile.acidity distribution is normal. The median is 7.9.

```{r echo=FALSE, warning=FALSE, volatile.acidity}
feature<-redwine_data$volatile.acidity
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.02)+
  scale_x_continuous(lim = c(0,1.6), breaks = seq(0,1.6,0.05))+
  xlab('volatile.acidity (g / cm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)

```
The volatile.acidity distribution is bimodal with the volatile.acidity peaking 
at 0.4, 0.5 and 0.6.
 
 
```{r echo=FALSE, warning=FALSE, citric.acid}

feature<-redwine_data$citric.acid
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.01)+
  scale_x_continuous(lim = c(0,0.75), breaks = seq(0,0.75,0.02))+
  xlab('citric.acid (g / dm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
table(feature)
```
 The distribution for citric acid appears bimodal with the peaking at 0, 0.24, 
 0.49.
 
```{r echo=FALSE, warning=FALSE, sugar}

feature<-redwine_data$sugar
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.1)+
  xlab('sugar (g / cm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
table(feature)
```
```{r echo=FALSE, warning=FALSE, sugarlog.10}

feature<-redwine_data$sugar
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.024)+
  scale_x_log10()+
  xlab('sugar (g / cm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
table(feature)
quantile(feature,.9)
```
Transform the long tail data to better understand the distribution of 
sugar
The distribution for sugar appears to be right skewed. Most of 
them (90%) sugar less  than 3.6 (4.5 g / cm^3 are considered sweet).
 
```{r echo=FALSE, warning=FALSE, chlorides}

feature<-redwine_data$chlorides
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.002)+
  xlab('chlorides (g / cm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)

```

```{r echo=FALSE, warning=FALSE, chlorides.log.10}

ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.024)+
  scale_x_log10()+
  xlab('chlorides (g / cm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
quantile(feature,.95)

```
Transform the long tail data to better understand the distribution of chlorides
The distribution for chlorides appears to be right skewed. Most of them (95%) 
chlorides less than 0.1261 .


```{r echo=FALSE, warning=FALSE, free.SO2}

feature<-redwine_data$free.SO2
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 2)+
  xlab('free.SO2  (mg / dm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
quantile(feature,.95)

```
```{r echo=FALSE, warning=FALSE, sqrt.free.SO2 }

ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.4)+
  scale_x_sqrt(lim = c(1,80),breaks = seq(0,100,5))+
  xlab('free.SO2 (mg / dm^3)') + ylab('Number of observations')
summary(feature)
quantile(feature,.95)

```
Transform the long tail data to better understand the distribution of 
free.SO2
The free.SO2 distribution is bimodal with the free.SO2 
peaking at 7 and 17.
 


```{r echo=FALSE, warning=FALSE, total.SO2}

feature<-redwine_data$total.SO2
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 2)+
  xlab('total.SO2  (mg / dm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
quantile(feature,.95)

```
```{r echo=FALSE, warning=FALSE, total.SO2log.10}
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.1)+
  scale_x_log10(lim = c(1,200),breaks = seq(0,200,40))+
  xlab('total.SO2 (mg / dm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
quantile(feature,.95)

```
Transform the long tail data to better understand the distribution of 
total.SO2
The total.SO2 distribution is normal.
 

```{r echo=FALSE, warning=FALSE, pH}

feature<-redwine_data$pH
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.02)+
  xlab('pH)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
table(feature)
```
The pH distribution is normal.

```{r echo=FALSE, warning=FALSE, density}

feature<-redwine_data$density
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.001)+
  scale_x_continuous(lim = c(0.990,1.005), breaks = seq(0.990,1.005,0.002))+
  xlab('Density (g / cm^3)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
```
 The distribution for density acid appears to be normal and the different 
 between min and max is only 0.014. ( different between alcohol and water 
 is 0.22)
 
 Ref : https://en.wikipedia.org/wiki/Ethanol
 
```{r echo=FALSE, warning=FALSE, sulphates}

feature<-redwine_data$sulphates
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.04)+
  scale_x_continuous(lim = c(0.3,2.0), breaks = seq(0.3,2.0,0.1))+
  xlab('Sulphates (potassium sulphate - g / dm3)') + 
  ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)


```

```{r echo=FALSE, warning=FALSE, log10.sulphates }

feature<-redwine_data$sulphates

ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.04)+
  scale_x_log10()+
  xlab('Sulphates (potassium sulphate - g / dm3)') + 
  ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)
summary(feature)
quantile(feature,.95)
```
Transform the long tail data to better understand the distribution of sulphates.
The distribution for sulphates appears to be normal. Most of them (95%) 
sulphates less than 0.93.

 
```{r echo=FALSE, warning=FALSE, alcohol}

feature<-redwine_data$alcohol
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.1)+
  scale_x_continuous(lim = c(8,13), breaks = seq(8,13,0.2))+
  xlab('alcohol (% by volume)') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)

summary(feature)
```

The distribution for alcohol appears to be right skewed.


```{r echo=FALSE, warning=FALSE, quality}

feature<-redwine_data$quality
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 1)+
  xlab('WineQuality') + ylab('Number of observations')+ 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)

table(feature)
nrow(subset(redwine_data,quality >4 & quality < 8)) / nrow(redwine_data)
```

Most of data's wine qulity is between 5 to 7 (94.9 %). I think I will covert 
this feature to factor for Multivariate Analysis.



# Univariate Analysis
 
### What is the structure of your dataset?

ANS :
There are 1599 wine in the data set with 12 features.
```{r echo=FALSE}
str(redwine_data)
summary(redwine_data)
head(redwine_data)
```

Input variables (based on physicochemical tests):
1. - fixed acidity (tartaric acid - g / dm^3): most acids involved with wine or 
fixed or nonvolatile (do not evaporate readily)
2. - *volatile acidity (acetic acid - g / dm^3): the amount of acetic acid in 
wine, which at too high of levels can lead to an unpleasant, vinegar taste
3. - *citric acid (g / dm^3): found in small quantities, citric acid can add 
'freshness' and flavor to wines
4. - residual sugar (g / dm^3): the amount of sugar remaining after fermentation
stops, it's rare to find wines with less than 1 gram/liter and wines with 
greater than 45 grams/liter are considered sweet
5. - chlorides (sodium chloride - g / dm^3): the amount of salt in the wine
6. - free sulfur dioxide (mg / dm^3): the free form of SO2 exists in equilibrium
between molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents
microbial growth and the oxidation of wine
7. - *total sulfur dioxide (mg / dm^3): amount of free and bound forms of S02;
in low concentrations, SO2 is mostly undetectable in wine, but at free SO2
concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine
8. - *density (g / cm^3)
9. - pH: describes how acidic or basic a wine is on a scale from 0 (very acidic)
to 14 (very basic); most wines are between 3-4 on the pH scale
10. - sulphates (potassium sulphate - g / dm3): a wine additive which can
contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial
and antioxidant
11. - alcohol (% by volume): the percent alcohol content of the wine

Output variable (based on sensory data): 
12. - quality (score between 0 and 10)


### What is/are the main feature(s) of interest in your dataset?
ANS: The main feature of interest is wine's quality. I would like to investigate
which variable(s) effect the wine quality.



### What other features in the dataset do you think will help support your
investigation into your feature(s) of interest?
ANS: I think smell taste touch and addictive content that will effect the wine's
quality so the features that I choose for investigation is :

1) sulphates
2) volatile acidity
3) citric acidity
4) chlorides 
6) sum of acid (tartaric acid + citric acid ) as "sourness"
5) alcohol

```{r echo=FALSE}
#https://en.wikipedia.org/wiki/Taste
redwine_data$sourness = redwine_data$fixed.acidity*0.7 + 
  redwine_data$citric.acid*0.46 
head(redwine_data)
```


### Did you create any new variables from existing variables in the dataset?

Yes, I create "sourness"  from fixed.acidity and citric.acid that represent the 
sourness of wine.

### Of the features you investigated, were there any unusual distributions? Did 
you perform any operations on the data to tidy, adjust, or change the form of 
the data? If so, why did you do this?


ANS: The distribution for citric acid, volatile.acidity and free.SO2 
appears bimodal and I tidies the data by remove X feature  that I am not 
interested and transform fixed.acidity and citric.acid to sourness for next 
investigation.


# Bivariate Plots Section

```{r echo=FALSE }
set.seed(1112)
data_all_subset <-redwine_data
names(data_all_subset)[1] <- c("TAC")#fixed.acidity 
names(data_all_subset)[2] <- c("acetic")#volatile.acidity
names(data_all_subset)[3] <- c("citric")#citric.acid
names(data_all_subset)[5] <- c("salt")#chlorides
names(data_all_subset)[6] <- c("f.SO2")#free.SO2
names(data_all_subset)[7] <- c("t.SO2")#total.SO2
names(data_all_subset)[8]<- c("D")#density
names(data_all_subset)[10]<- c("K2SO4")#sulphates
names(data_all_subset)[13]<- c("sour")#sourness

ggcorr(data_all_subset, nbreaks = 4, palette = "RdGy", label = TRUE, 
       label_size = 6, label_color = "white")

ggpairs(data_all_subset, 
        upper = list(continuous = wrap(ggally_cor, size = 6)))+ 
  theme(axis.line=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

```

Top correlation values for quality is :
1. alcohol : 0.476
2. volatile.acidity : -0.391
3. sulphates : 0.251
4. citric acid : 0.226

```{r  echo=FALSE}
build_bivarate_plot <- function(data,x, y, ylab,xlab) {
  return (ggplot(data = data, aes(x = x, y = y)) + geom_boxplot() +  
            ylab(ylab) + xlab(xlab)
  )
}
redwine_data$wine_rating <- ifelse(redwine_data$quality <= 5, 'normal', 
                                   ifelse( redwine_data$quality < 7,
                                           'good', 'excellent'))
redwine_data$wine_rating <- ordered(redwine_data$wine_rating,levels = 
                                      c('normal', 'good', 'excellent'))
```

```{r  echo=FALSE, WineQuality.vs.volatile.acidity}
feature <- redwine_data$volatile.acidity
feature_name <- 'volatile.acidity (g / cm^3)'
plot_title = "Red wine Volatile Acidity by Wine Rating"
volatile.acid.V.wine_rating.plot<- build_bivarate_plot(
  redwine_data, redwine_data$wine_rating, feature ,
  feature_name,'Wine Rating')+
  scale_y_continuous(lim = c(0,1.6), breaks = seq(0,1.6,0.2))+ 
  ggtitle(plot_title)  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
volatile.acid.V.wine_rating.plot
with(redwine_data, cor.test(feature, quality, method = 'pearson'))

```
### WineQuality.vs.citric.acid
```{r  echo=FALSE }
feature <- redwine_data$citric.acid
feature_name <- 'citric.acid (g / cm^3)'
plot_title = "Red wine Citric acid by Wine Rating"
citric.acid.V.wine_rating.plot<- build_bivarate_plot(
  redwine_data, redwine_data$wine_rating, feature ,feature_name,'Wine Rating')+ 
  ggtitle(plot_title)  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
citric.acid.V.wine_rating.plot

with(redwine_data, cor.test(feature, quality, method = 'pearson'))


```

### WineQuality.vs.sulphates
```{r  echo=FALSE }
feature <- redwine_data$sulphates
plot_title = "Red wine Potassium Sulphate by Wine Rating"
feature_name <- 'Potassium Sulphate (g /dm^3)'
sulphates.V.wine_rating.plot<-build_bivarate_plot(
  redwine_data, redwine_data$wine_rating, feature ,feature_name,'Wine Rating')+
  scale_y_continuous(lim = c(0.25,1), breaks = seq(0.25,1,0.05))+
    ggtitle(plot_title)  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
sulphates.V.wine_rating.plot
with(redwine_data, cor.test(feature, quality, method = 'pearson'))




```


### WineQuality.vs.alcohol
```{r  echo=FALSE }
feature <- redwine_data$alcohol
feature_name <- 'alcohol (% by volume)'
plot_title = "Red wine % alcohol by Wine Rating" 
alcohol.V.wine_rating.plot<-build_bivarate_plot(
  redwine_data, redwine_data$wine_rating, feature ,feature_name,'Wine Rating')+
  scale_y_continuous(lim = c(8,15), breaks = seq(8,15,0.5))+ 
  ggtitle(plot_title)  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
with(redwine_data, cor.test(feature, quality, method = 'pearson'))
alcohol.V.wine_rating.plot
```


# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the
### investigation. How did the feature(s) of interest vary with other features 
### in the dataset?  
ANS: From the plots and correlation values sulphates, citric acid acidity, 
alcohol positively relate with quality but volatile acidity negatively relate 
with quality.

Alcohol sulphates and volatile acidity 's plot show the different between 3 wine
rating of wine very well but citric acid show the different between normal 
and good wine poorly.


### Did you observe any interesting relationships between the other features 
(not the main feature(s) of interest)?

```{r echo=FALSE,warning=FALSE, Multivariate_Plots}

build_bivarate_plot2 <- function(data,x, y, xlab,ylab) {
  return (
          ggplot(aes(x = x, y = citric.acid), data = data) +
            geom_point( alpha =  1/2 ) +
            xlab(xlab) + ylab(ylab)+
            geom_smooth()
  )
}

featureX <- redwine_data$volatile.acidity
featureX_name <- 'volatile.acidity (g/cm^3)'
featureY <- redwine_data$citric.acid
featureY_name <- 'citric.acid (g/cm^3)'

build_bivarate_plot2(redwine_data, featureX, featureY ,featureX_name , 
                     featureY_name)+
  scale_x_continuous(lim = c(0.1,1.2), breaks = seq(0.1,1.2,0.1))+
  scale_y_continuous(lim = c(0,0.9), breaks = seq(0,0.9,0.1))

with(redwine_data, cor.test(featureX, featureY, method = 'pearson'))

featureX <- redwine_data$sulphates
featureX_name <- 'Potassium Sulphate (g /dm^3)'
featureY <- redwine_data$citric.acid
featureY_name <- 'citric.acid (g/cm^3)'

build_bivarate_plot2(redwine_data, featureX, featureY ,featureX_name , 
                     featureY_name)+
  scale_x_continuous(lim = c(0.1,1.2), breaks = seq(0.1,1.2,0.1))
with(redwine_data, cor.test(featureX, featureY, method = 'pearson'))

featureX <- redwine_data$alcohol
featureX_name <- 'alcohol'
featureY <- redwine_data$citric.acid
featureY_name <- 'citric.acid (g/cm^3)'

build_bivarate_plot2(redwine_data, featureX, featureY ,featureX_name , 
                     featureY_name)
with(redwine_data, cor.test(featureX, featureY, method = 'pearson'))


```
ANS: 
I found that citric acid and volatile acidity very correlate.  
  
#### High Corelation:  
citric acid and volatile acidity : -0.5524957  
citric acid and sulphates acidity : 0.31277   
  
#### Low Corelation:  
citric acid and alcohol acidity : 0.1099032  
  

### What was the strongest relationship you found?  
ANS: For feature of interest alcohol percentage has highest corelation value.
(0.476)  
     For every pair of features free.SO2 and total.SO2 
     has highest corelation value. (0.66  
  


# Multivariate Plots Section


First I need to prepare alcohol.level for multivariate plot.
```{r echo=FALSE}

redwine_data$alcohol.level <- ifelse(redwine_data$alcohol < 10, 
                                     'low alcohol', 
                                     ifelse( redwine_data$alcohol < 11.5, 
                                             'medium-low alcohol', 
                                             'medium alcohol'))
redwine_data$alcohol.level <- ordered(redwine_data$alcohol.level,levels = 
                                        c('low alcohol', 'medium-low alcohol', 
                                          'medium alcohol'))

```

```{r echo=FALSE }

cdatx <- ddply(redwine_data, "wine_rating", summarise, 
                volatile.acidity.median=median(volatile.acidity))
cdaty <- ddply(redwine_data, "wine_rating", summarise, 
                alcohol.median=median(alcohol))

plot_title = "Percent alcohol by volatile.acidity and Wine Rating with 
median lines"
ggplot(aes(x = volatile.acidity, y = alcohol,color = wine_rating), data = 
         redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('volatile.acidity (g/cm^3)') + ylab('% alcohol')+  
    geom_vline(data=cdatx, aes(xintercept=volatile.acidity.median,  
                              colour=wine_rating),
               linetype="dashed", size=2)+  
    geom_hline(data=cdaty, aes(yintercept=alcohol.median,  
                              colour=wine_rating),
               linetype="dashed", size=2)+
  scale_x_continuous(lim = c(0.1,1.3), breaks = seq(0.1,1.3,0.1))+
  scale_y_continuous(lim = c(8,15), breaks = seq(8,15,0.5))+
  geom_point(alpha = 1/5,size =5)+ 
  ggtitle(plot_title)  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))

  
```
  
From the plot show that the excellent wine mostly stay on the top left, 
good wine 
stay in the middle and normal wine stay in the bottom right.



```{r echo=FALSE,warning=FALSE }

wine_rating.v.alcohol.level.v.volatile.acidity.plot <- ggplot(
  aes(x = volatile.acidity ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('volatile.acidity (g/cm^3)') + ylab('Number of observations')+  
   scale_fill_brewer(type = 'qual')+
  scale_x_continuous(lim = c(0.1,1), breaks = seq(0.1,1,0.05))+
  geom_histogram()+facet_wrap(~alcohol.level,ncol = 1, scales="free_y")
wine_rating.v.alcohol.level.v.volatile.acidity.plot
```
  
Wine rating.vs.alcohol.level.vs.volatile.acidity plot shows that :
  
excellent wine ratio in alcohol grade "medium" on volatile.acidity range 
0.25-0.4 is very high.

```{r echo=FALSE,warning=FALSE }
wine_rating.v.alcohol.level.v.citric.acid.plot <- ggplot(
  aes(x = citric.acid ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('citric.acid (g/cm^3)') + ylab('Number of observations')+  
  scale_fill_brewer(type = 'qual')+
  scale_x_continuous(lim = c(0,0.9), breaks = seq(0,0.9,0.1))+
  geom_histogram()+facet_wrap(~alcohol.level,ncol = 1, scales="free_y")
wine_rating.v.alcohol.level.v.citric.acid.plot
```
  
Wine rating.vs.alcohol.level.vs.citric.acid plot shows that the excellent wine 
ratio in alcohol grade "medium" on citric.acid at 0 and 0.4 is very high.


```{r echo=FALSE,warning=FALSE }
wine_rating.v.alcohol.level.v.total.SO2.plot <- ggplot(
  aes(x = total.SO2 ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('total.SO2 (mg/dm^3)') + ylab('Number of observations')+ 
  scale_fill_brewer(type = 'qual')+
  geom_histogram()+facet_wrap(~alcohol.level,ncol = 1, scales="free_y")+
  scale_x_continuous(lim = c(0,170), breaks = seq(0,170,5))
wine_rating.v.alcohol.level.v.total.SO2.plot
```
  
Wine rating.vs.alcohol.level.vs.total.SO2 plot shows that the excellent 
wine ratio in alcohol grade "medium" on total.SO2 at 5-30 is very 
high.


```{r echo=FALSE,warning=FALSE, wine.rating.vs.alcohol.level.vs.sulphates }

wine_rating.v.alcohol.level.v.sulphates.plot <- ggplot(
  aes(x = sulphates ,fill = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('Potassium Sulphate (g /dm^3)') + ylab('Number of observations')+  
  scale_fill_brewer(type = 'qual')+
  scale_x_continuous(lim = c(0.35,1), breaks = seq(0.35,1,0.05))+
  geom_histogram()+facet_wrap(~alcohol.level,ncol = 1, scales="free_y")
wine_rating.v.alcohol.level.v.sulphates.plot

```
  
Wine rating.vs.alcohol.level.vs.sulphates plot shows that the excellent wine 
ratio in alcohol grade "medium" on sulphates range 0.7-0.9 is very high.


```{r echo=FALSE,warning=FALSE  }

wine_rating.v.alcohol.level.v.sourness.chlorides.plot <- ggplot(
  aes(x = sourness, y = chlorides,color = wine_rating), data = redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('sourness') + ylab('chlorides')+
  geom_point(alpha = 1/3,size =3)+facet_wrap(~alcohol.level,ncol = 1)
wine_rating.v.alcohol.level.v.sourness.chlorides.plot
  

```
    
Pattern is not noticable here.  


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the 
investigation. Were there features that strengthened each other in terms of 
looking at your feature(s) of interest?

From the plots , show that alcohol feature is the highest impact feature.  

Wine rating.vs.alcohol.level.vs.volatile.acidity plot shows that excellent wine 
ratio in alcohol grade "medium" on volatile.acidity range 0.25-0.4 is very high.  
Wine rating.vs.alcohol.level.vs.citric.acid plot shows that excellent wine ratio
in alcohol grade "medium" on citric.acid at 0 and 0.35-0.5 is very high.  
Wine rating.vs.alcohol.level.vs.total.SO2 plot shows that excellent
wine ratio in alcohol grade "medium" on total.SO2 at 5-30 is very 
high.  
Wine rating.vs.alcohol.level.vs.sulphates plot shows that excellent wine ratio 
in alcohol grade "medium" on sulphates range 0.7-0.9 is very high.  
Win rating.vs.alcohol.level.vs.sourness.vs.chlorides shows that there hardly to 
determine wine quality by tongue (chorides and sourness).  


### Were there any interesting or surprising interactions between features?  

It is very surprise that smell(total.SO2) has influnce over the wine 
rating but taste(chorides and sourness) has not.  


------

# Final Plots and Summary

### Plot One 
  
##### Alcohol Distribution


```{r echo=FALSE, Plot_One : Alcohol.distribution}

feature<-redwine_data$alcohol
ggplot(redwine_data)+geom_histogram(aes(x =feature),binwidth = 0.2, 
                                    color = I('black'), fill = I('#F79420') )+
  scale_x_continuous(lim = c(8,15), breaks = seq(8,15,0.5))+
  xlab('Alcohol (% by volume)') + ylab('Number of observations') + 
  geom_vline(xintercept=quantile(feature,0.05), color="red",linetype = 2)+ 
  geom_vline(xintercept=median(feature), color="red",linetype = 1)+ 
  geom_vline(xintercept=quantile(feature,0.95), color="red",linetype = 2)+ 
  ggtitle("Red wine Persent alcohol distribution")  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))

summary(redwine_data$alcohol)

```
 
### Description One

 The distribution for alcohol appears right skewed with the median at 10.2 % and
 90% of red wines data have alcohol between 9.2% to 12.5%, perhaps due to the 
 demand of red wines and buyers purshasing make the plot look like this.
 
 

### Plot Two

#### How does each features influence the wine rating ?
```{r echo=FALSE, Bivariate_Plots}
grid.arrange(alcohol.V.wine_rating.plot,sulphates.V.wine_rating.plot,
             citric.acid.V.wine_rating.plot,volatile.acid.V.wine_rating.plot)

data_all_subset <-redwine_data[,c(11,10,3,2,12)]
ggpairs(data_all_subset, 
        upper = list(continuous = wrap(ggally_cor, size = 6)))+ 
  theme(axis.line=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

ggcorr(data_all_subset, nbreaks = 4, palette = "RdGy", label = TRUE, 
       label_size = 6, label_color = "white",label_round = 3)

```

### Description Two

Alcohol percentage, sulphates, citric acid correlate with wine rating positively
but volatile acidity correlate negatively.

Red wines's rating is corelate with these feature order following:  

(strong)-------------------------------------->(weak)  
alcohol > volatile.acidity > sulphates > citric acid 




### Plot Three

#### What makes wine excellent ?

```{r echo=FALSE,warning=FALSE,  Plot_Three}

cdatx <- ddply(redwine_data, "wine_rating", summarise, 
                volatile.acidity.median=median(volatile.acidity))
cdaty <- ddply(redwine_data, "wine_rating", summarise, 
                alcohol.median=median(alcohol))

plot_title = "3.1 Percent alcohol by volatile.acidity and 
Wine Rating with median lines"
ggplot(aes(x = volatile.acidity, y = alcohol,color = wine_rating), data = 
         redwine_data) +
  #geom_point( alpha =  1/2 ) +
  xlab('volatile.acidity (g/cm^3)') + ylab('% alcohol')+  
    geom_vline(data=cdatx, aes(xintercept=volatile.acidity.median,  
                              colour=wine_rating),
               linetype="dashed", size=2)+  
  scale_x_continuous(lim = c(0.1,1.3), breaks = seq(0.1,1.3,0.1))+
  scale_y_continuous(lim = c(8,15), breaks = seq(8,15,0.5))+
  geom_point(alpha = 1/4,size =3)+ 
  ggtitle(plot_title)  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))


plot_final_hist <- function(data,plot_title) {
  focus_feature_all_data = redwine_data$sulphates
  focus_feature_target_data = data$sulphates
  
  cdat <- ddply(data, "wine_rating", summarise, 
                sulphates.median=median(sulphates))
  return (
ggplot(aes(x = sulphates ,fill = wine_rating), data = data) +
  xlab('Potassium Sulphate (g /dm^3)') + 
  ylab('Number of observations')+  
    geom_vline(data=cdat, aes(xintercept=sulphates.median,  
                              colour=wine_rating),
               linetype="dashed", size=1)+
  scale_x_log10(lim = c(0.3,1), breaks = seq(0.3,1,0.05))+
  geom_histogram(alpha=.5, position="identity")+ 
  ggtitle(plot_title)  + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
  )
}


low_al_data <- subset(redwine_data,
                 redwine_data$alcohol.level == "low alcohol")
lm_al_data <- subset(redwine_data,
                 redwine_data$alcohol.level == "medium-low alcohol")
m_al_data <- subset(redwine_data,
                 redwine_data$alcohol.level == "medium alcohol")

#"Red wine Persent alcohol / Volatile Acidity by Wine rating"



low_al_plot <- plot_final_hist(low_al_data,"3.2.1 Low Alcohol Red wines 
Distribution of 
                Potassium sulphase by Wine rating with median lines")

m_low_al_plot <- plot_final_hist(lm_al_data,"3.2.2 Medium-low Alcohol 
Red wines Distribution 
                of Potassium sulphase by Wine rating with median lines")

m_al_plot <- plot_final_hist(m_al_data,"3.2.3 Medium Alcohol Red wines 
Distribution of 
                Potassium sulphase by Wine rating with median lines")

grid.arrange(low_al_plot,m_low_al_plot,m_al_plot)

summary(lm_al_data$wine_rating)
summary(low_al_data$wine_rating)
summary(m_al_data$wine_rating)


```

### Description Three
From plot 3.1 shows that redwines that have low volatile acidity and high 
% alocohol tend to have higher rating.
From plot 3.2.1-3.2.3 the excellent quality redwines have highest median 
potassium 
sulphase and the 
proportion of excellent redwines are greater in medium alcohol level compare
 to the proportion of redwines in other alcohol level.


------

# Reflection

```{r echo=FALSE}
str(redwine_data)
```

The data set contain 1599 wine from 2009. I start by understand the distribution
 and variables in data set and try to interpret in term of sense that human can 
 percieve. First I found that the distribution of alcohol is right skewed,I 
 believe that the demands of rewine drive this distribution. From bivariate and
 multivariate analytsis, I found that the taste sourness and salty has 
 no evidence that they has influence over the quality of wine but the smell 
(total sulfur dioxide), addictive content (alcohol), voilatile acidity, citric 
acid and sulphates has influence over it. On low alcohol percentage we hardly 
found excellent wine_rating but mostly is normal and you can find some of good 
wine rating if they has total SO2 in range 5-60 and sulphates in range 0.53-0.73
,On medium-low alcohol percentage wine exellent can be found on low volatile 
acidity and total sulfur dioxide below 55 but mostly are normal and good rating 
wine,On medium alcohol percentage exellent red wine can be found at high 
percentage on total sulfur dioxide below 50 and sulphate upper than 0.65 and 
mostly are exellent and good rating wine. I struggled to visulize multivariate 
plot to clearly present the relation more than one featue against wine quality 
at first finally I found out that if I create new varible that represent the 
feature as group It will be easier,Next I can not clearly present the 
relation of selected features by geom_point as you can see non of features has 
strong corelation value but this become much better when I decide to 
use histogram.  
After I research(google) and ask a drinker,my friend, I found out that there are
many significant variables that we do not have such as type of grape, 
where it made from, age of wine.
I am confident that if the data had these variables, I could provide more 
insightful 
analysis over red wine quality.
