pseudo facebook Data
```{r}
getwd()
setwd('~/WorkSpace/Udemy-Datascience/IntroductionToDataScience/EDA-DataAnalyse/L3')
list.files()

pf <- read.csv('pseudo_facebook.tsv',sep = '\t')
pf2 <- read.delim('pseudo_facebook.tsv')
names(pf)
```

Histogram of Users' Birthdays
```{r}
install.packages("ggplot2", dep = TRUE)

install.packages('ggthemes', dependencies = TRUE)
```

Estimate Audience size
```{r}
library(ggplot2)
theme_set(theme_minimal(24))
qplot(x = dob_day,data = pf) + stat_count(width = 0.5) + scale_x_discrete(breaks = 1:31)

ggplot(aes(x = dob_day), data = pf) + 
  stat_count(width = 0.5) + 
  scale_x_discrete(breaks = 1:31)
```

```{r}
ggplot(data = pf, aes(x = dob_day)) + 
  scale_x_discrete(breaks = 1:31) +
  stat_count(width = 0.5) + 
  facet_wrap(~dob_month,ncol=3)
```

## Friend Count
```{r}
qplot(x = friend_count, data = pf)
qplot(x = friend_count, data = pf, xlim= c(0,1000))

ggplot(data = pf, aes(x = friend_count))+geom_histogram()

less2000fr_records = nrow(subset(pf,friend_count < 2000 ))
pf_records = nrow(pf)
percent_less2000 = less2000fr_records*100/pf_records

ggplot(data = pf, aes(x = friend_count) )+geom_histogram()+ 
  scale_x_continuous(limits = c(0,1000))

qplot(x = friend_count, data = pf, xlim= c(0,1000))
qplot(x = friend_count, data = pf, xlim= c(0,1000),binwidth = 25)

qplot(x = friend_count, data = pf, xlim= c(0,1000),binwidth = 200)

qplot(x = friend_count, data = pf, xlim= c(0,1000),binwidth = 25) + scale_x_continuous(limits = c(0, 1000),breaks = seq(0,1000,50))
```
Omitting NA Observations

```{r}
qplot(x = friend_count, data = pf, xlim= c(0,1000),binwidth = 25,xlab = seq(0,1000,50)) + facet_wrap(~gender)

qplot(x = friend_count, data = subset(pf, !is.na(gender)), xlim= c(0,1000),binwidth = 25,xlab = seq(0,1000,50)) + facet_wrap(~gender)

qplot(x = friend_count, data = na.omit(pf), xlim= c(0,1000),binwidth = 25,xlab = seq(0,1000,50)) + facet_wrap(~gender)
```

 Statistics 'by' Gender
 
 
```{r}
table(pf$gender)
summary_gender_friend_count<-by(pf$friend_count,pf$gender,summary)
summary_gender_friend_count
names(summary_gender_friend_count)
```
Which gender on average has more friends?
```{r}
median_male = summary_gender_friend_count$male[3]
median_female = summary_gender_friend_count$female[3]
median_male
median_female
```

What's the diff between the median friend count for women and men?
```{r}
names(median_male)
median_male_val = summary_gender_friend_count$male[3][[1]]
median_female_val = summary_gender_friend_count$female[3][[1]]
median_female_val - median_male_val
```
Tenure
```{r}
ggplot(aes(x = tenure), data = pf) + geom_histogram( binwidth = 30, color = 'black', fill = '#099DD9')
ggplot(aes(x = tenure/365), data = pf) + geom_histogram( binwidth = .25, color = 'black', fill = '#F79420')

ggplot(aes(x = tenure/365), data = pf) + geom_histogram( binwidth = .25, color = 'black', fill = '#F79420') + scale_x_continuous(breaks = seq(1,7,1), lim = c(0,7))

qplot( x = tenure/365, data = pf, binwidth =.25, color = I('black'), fill = I('#F79420') ) + scale_x_continuous(breaks = seq(1,7,1), lim = c(0,7)) + xlab('Number of years using Facebook') + ylab('Number of users in sample')
```

User.ages
```{r}
qplot( x = age, data = pf, binwidth =5, color = I('black'), fill = I('#F79420') ) + scale_x_continuous(breaks = seq(0,120,5), lim = c(0,150)) + xlab('Age of user using Facebook') + ylab('Number of users in sample')

qplot( x = age, data = pf, binwidth =1, color = I('black'), fill = I('#F79420') ) + scale_x_continuous(breaks = seq(0,120,5), lim = c(0,120)) + xlab('Age of user using Facebook') + ylab('Number of users in sample')
```

Transforming data

```{r}
qplot(x = friend_count ,data = pf)
summary(pf$friend_count)
summary(log10(pf$friend_count))
summary(log10(pf$friend_count + 1))
summary(sqrt(pf$friend_count + 1))

install.packages('gridExtra')
library(gridExtra)
graph1 <- qplot(x = friend_count ,data = pf) +scale_y_log10()
graph2 <- qplot(x = friend_count ,data = pf) +scale_y_sqrt()
grid.arrange( graph1, graph2, ncol=2)

graph0 <- qplot(x = friend_count ,data = pf) 
graph1 <- qplot(x = log10(friend_count+1) ,data = pf) 
graph2 <- qplot(x = sqrt(friend_count) ,data = pf) +scale_y_sqrt()
grid.arrange( graph0, graph1, graph2)

graph1 <- graph0 +scale_x_log10()
```

 #### Frequency Polygons

```{r}
qplot(x = friend_count ,data = subset(pf, !is.na(gender) ), binwidth = 10 )  + scale_x_continuous(lim = c(0,1000), breaks = seq(0,1000,50)) + facet_wrap(~gender)

qplot(x = friend_count ,data = subset(pf, !is.na(gender) ), binwidth = 10 ,geom = 'freqpoly', color = gender)  + scale_x_continuous(lim = c(0,1000), breaks = seq(0,1000,50))

qplot(x = friend_count , y = ..count../sum(..count..),
      data = subset(pf, !is.na(gender) ), binwidth = 10 ,
      xlab = 'Friend Count sqrt',
      ylab = 'Proportion of Users with that friend count sqrt',
      geom = 'freqpoly', color = gender) +scale_x_sqrt() +
      scale_x_continuous(lim = c(0,71), breaks = seq(0,71,10))

summary(pf$friend_count)
summary(log10(pf$friend_count+1))
summary(sqrt(pf$friend_count))


summary(pf$www_likes)
summary(log10(pf$www_likes+1))
summary(sqrt(pf$www_likes))

qplot(x = www_likes , 
      data = subset(pf, !is.na(gender) ) ,
      xlab = 'Like Count',
      ylab = 'Proportion of Users with that Like count sqrt',
      geom = 'freqpoly', color = gender) +
      scale_x_continuous()+scale_x_log10()

sum_wwlike <- by(pf$www_likes,pf$gender, sum)

sum_wwlike['female'][[1]] - sum_wwlike['male'][[1]]


```

### Box Plots
```{r}
summary(subset(subset(pf, !is.na(gender)), friend_count  < 1000 )$friend_count)
friend_count_less1000 = subset(subset(pf, !is.na(gender)), friend_count  < 1000 )
qplot(x = gender,y = friend_count ,
      data = friend_count_less1000,
      geom = 'boxplot') 

qplot(x = gender,y = friend_count ,
      data = subset(pf, !is.na(gender)), ylim = c(0,1000),
      geom = 'boxplot') 


qplot(x = gender,y = friend_count ,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot') + scale_y_continuous(limits = c(0,1000))

qplot(x = gender,y = friend_count ,
      data = subset(pf, !is.na(gender)),
      geom = 'boxplot') + coord_cartesian(ylim = c(0,250))
by(pf$friend_count, pf$gender, summary)
```
Getting Logiccal
```{r}
pf$mobile_check_in <- NA
pf$mobile_check_in <- ifelse(pf$mobile_likes >0 , 1 , 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
by(pf$mobile_check_in, pf$gender, summary)

sum_mobile_cin = summary(pf$mobile_check_in)
sum_mobile_cin[2][[1]] / (sum_mobile_cin[1][[1]] + sum_mobile_cin[2][[1]])

```

### Problem Set 3 
```{r}
library(ggplot2)
data(diamonds)
summary(diamonds)
names(diamonds)
diamonds
is.factor(diamonds$cut)
is.factor(diamonds$color)
is.factor(diamonds$clarity)
?diamonds
qplot(x = price, data = diamonds)
summary(diamonds$price)

nrow(subset(diamonds, price < 500))
nrow(subset(diamonds, price < 250))
nrow(subset(diamonds, price >= 15000))

### http://www.cookbook-r.com/Graphs/Facets_(ggplot2)

qplot(x = price, data = diamonds , binwidth = 1000 )+scale_x_continuous(lim = c(0,15000), breaks = seq(0,15000,2500))+ facet_wrap(~cut, scales="free_y") 

ggsave('priceHistogram.png')

by(diamonds$price, diamonds$cut, summary)
subset(diamonds, !is.na(diamonds$price))

summary(log10(diamonds$price))

qplot(x = price, data = diamonds , binwidth = 0.03) + scale_x_log10()+ facet_wrap(~cut, scales="free_y") 

qplot(x = cut,y = price ,data =diamonds,geom = 'boxplot')+scale_y_continuous(lim = c(0,6000))
ggsave('priceHistogram_cut.png')

qplot(x = color,y = price ,data =diamonds,geom = 'boxplot')+scale_y_continuous(lim = c(0,6000))
ggsave('priceHistogram_color.png')

qplot(x = clarity,y = price ,data =diamonds,geom = 'boxplot')+scale_y_continuous(lim = c(0,6000))
ggsave('priceHistogram_clarity.png')


names(diamonds)
by(diamonds$price, diamonds$color, summary)

diamon_j = subset(diamonds,diamonds$color == 'J')
diamon_d = subset(diamonds,diamonds$color == 'D')
summary(diamon_j$price)
summary(diamon_d$price)
IQR(diamon_j$price)
IQR(diamon_d$price)
?diamonds

diamonds$price_per_carat <- NA
diamonds$price_per_carat <- diamonds$price / diamonds$carat 
by(pf$mobile_check_in, pf$gender, summary)

qplot(x = color,y = price_per_carat ,data =diamonds,geom = 'boxplot')
ggsave('price_per_carat_Histogram_color.png')


summary(diamon_d$carat)
qplot(x = carat , data = diamonds , binwidth = 0.01 ,geom = 'freqpoly')  + scale_x_continuous(lim = c(0,1.1), breaks = seq(0,3.4,0.1))+
  scale_y_continuous(lim = c(0,9000), breaks = seq(0,9000,1000))

table(diamonds$carat)
```

# The Gapminder website contains over 500 data sets with information about
# the world's population. Your task is to download a data set of your choice
# and create 2-5 plots that make use of the techniques from Lesson 3.

```{r}
install.packages("xlsx", dep = T)      # If you have not installed it before
install.packages("dplyr", dep = T) 
install.packages("tidyr", dep = T) 

library(xlsx)
library(dplyr)
library(tidyr)
# Load Data
# http://data.worldbank.org/indicator/NY.GDP.MKTP.KD
gdp_data <- read.xlsx("indicator GDP at market prices, constant 2000 US$ (WB estimates) .xls.xlsx", sheetIndex = 1)
summary(gdp_data)

#data wranging
dplyr::tbl_df(gdp_data)
data_parse <- tidyr::gather(gdp_data,"year","gdp",2:53)
names(data_parse)
names(data_parse)[1]<-"country"
data_parse <- within(data_parse, { year=as.POSIXct(year, format = "X%Y") })
data_parse$year =  as.numeric(format(data_parse$year, "%Y"))
data_parse$year_factor  <- factor(data_parse$year)
# Plot gdp histogram in 2011
# Q What kind of gdp distribution is it?
qplot(x = gdp, data = subset(data_parse,!is.na(gdp) & year == 2010),
      xlab = 'GDP',
      ylab = 'Country Count', 
      color = I('black'), fill = I('#099DD9') )
ggsave('gdp_histogram_2010.png')

qplot(x = gdp, data = subset(data_parse,!is.na(gdp) & year == 2010),
      xlab = 'GDP',
      ylab = 'Country Count', 
      color = I('black'), fill = I('#F79420') )+ scale_x_log10()
ggsave('log10_gdp_histogram_2010.png')

# ANS : The result show that the data's distribution of GDP scale in 2010 is normal on logarithmic scale.

# Now I am focusing on  United States India Egypt Germany Australia United Kingdom China and Japan to determine Which one are tentative to be much higher GDP in next few years
summary(data_parse$country)
data_parse_f2 = subset(data_parse,
    country == "United States" |
    country == "India" | 
    country == "Egypt" | 
    country == "Germany" | 
    country == "Australia" | 
    country == "United Kingdom" |
    country == "China" | 
    country == "Japan")
# Q Which country are tentative to has high GDP in after 2010
qplot(x = year, y = gdp, data = subset(data_parse_f2,!is.na(gdp)),
      xlab = 'Year', geom = 'line', color = country) + scale_y_log10()
ggsave('log10_gdp_line_history_compare.png')
# ANS: You can see that China's plot is very impressive the slope is obviously higher than all of the selected countries.


summary(log10(data_parse$gdp))

# Does the overall gdp are continuously increasing.
selected_data = subset(data_parse,data_parse$year > 2000 & data_parse$year < 2011 & !is.na(data_parse$gdp))
qplot(x = year_factor, y= log10(gdp), data = selected_data,
      xlab = 'Year',
      geom = 'boxplot')

qplot(x = year_factor, y= log10(gdp), data = selected_data,
      xlab = 'Year',
      geom = 'boxplot')+ coord_cartesian(ylim = c(9,11))
ggsave('log10_gdp_boxplot_trend.png')

by(log10(selected_data$gdp), selected_data$year_factor, summary)
# ANS Yes.
#
```
Exploring Your Friends' Birthdays
```{r}
getwd()
setwd('~/WorkSpace/Udemy-Datascience/IntroductionToDataScience/EDA-DataAnalyse/L3')
library(ggplot2)

birthdayData <- read.csv("birthdaysExample.csv")
birthdayData$dates
birthdayData$date_obj <- strptime(birthdayData$dates,"%m/%d/%y")
help(as.Date)

birthdayData$dob_month <- factor(format(birthdayData$date_obj, "%b"))
birthdayData$dob_day <- as.numeric(format(birthdayData$date_obj, "%d"))
birthdayData$dob_month
birthdayData$dob_month <- ordered(birthdayData$dob_month, levels = c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

# How many people share your birthday? Do you know them?
# (Reserve time with them or save money to buy them a gift!)

# Which month contains the most number of birthdays?
# How many birthdays are in each month?

qplot(x = dob_month , data = birthdayData)

summary(birthdayData$dob_month)
ggsave('birthday_month_freq.png')
# ANS: March contains the most number of birthday.
# Jan Feb Mar Apr May Jun Jul Aug Sep Oct Nov Dec 
# 89  79  98  81  72  93  86  91  96  89  87  72 


# Which day of the year has the most number of birthdays?
ggplot(data = birthdayData, aes(x = dob_day)) + 
  scale_x_discrete(breaks = 1:31) +
  stat_count(width = 0.5) +  facet_wrap(~dob_month)
summary(birthdayData$date_obj)
#                 Min.               1st Qu.                Median                  Mean 
#"2014-01-01 00:00:00" "2014-03-28 00:00:00" "2014-07-02 00:00:00" "2014-06-30 09:59:25" 
#              3rd Qu.                  Max. 
#"2014-09-28 00:00:00" "2014-12-31 00:00:00" 
ggsave('birthday_day_freq.png')

# ANS : Follow the plot, 6-Feb, 22-May and 16-July have the most number of birthday (8).
help(qplot)


# Do you have at least 365 friends that have birthdays on everyday
# of the year?
#ANS : Follow the plot, No.


```

